Competing Constructions for German Measure Noun Phrases: from Usage Data to Experiment

### 2017-04-16 Latex/article.tex
Another release candidate.

Then, a multilevel logistic regression was specified with the probability of the \PGCa\ predicted for each sentence by the corpus-based GLMM as the only fixed effect \textit{Modelprediction}.%
\footnote{The document-level variables \textit{Badness} and \textit{Genitives} were set to 0, which is the mean for z-transformed variables.}
A random intercept and slope were added for the individual sentence (item) in order to catch idiosyncrasies of single sentences.
Also, a random intercept and slope for participants was added.%
\footnote{The random slopes were added to comply with \citet[257]{BarrEa2013} who predict \textit{catastrophically high Type I error rates} for experimental designs with within-subject manipulations if random effects structures are not kept maximal.
Notice that the model reported here was estimated with conceptually identical results with regard to the predictor of interest (\textit{Modelprediction}) if only random intercepts were used.}
Coefficients were estimated with Maximum Likelihood Estimation (\textit{lmer} function from \textit{lme4}).
The number of observations was \textit{n=}384.

>>>>

Then, a multilevel logistic regression was specified with the probability of the \PGCa\ predicted for each sentence by the corpus-based GLMM as the only fixed effect \textit{Modelprediction}.%
\footnote{The document-level variables \textit{Badness} and \textit{Genitives} were set to 0, which is the mean for z-transformed variables.}
A random intercept and slope were added for the individual sentence (item) in order to catch idiosyncrasies of single sentences.
Also, a random intercept and slope for participants was added.%
\footnote{The random slopes were added to comply with \citet[257]{BarrEa2013} who predict \textit{catastrophically high Type I error rates} for experimental designs with within-subject manipulations if random effects structures are not kept maximal.
Notice that the model reported here was estimated with conceptually identical results \wrt the predictor of interest (\textit{Modelprediction}) if only random intercepts were used.}
Coefficients were estimated with Maximum Likelihood Estimation (\textit{lmer} function from \textit{lme4}).
The number of observations was \textit{n=}384.
